Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-09-30 ms/ms.Rmd
ms: add bedrock to sites

At Skrimfjella we delineated a study area of \unit{34\,km^{2}} based on radiometric coverage and accessibility (Fig. \@ref(fig:sites)b).   
The landscape within our delineation is classified as *inland hills and mountains* [@simensenDiversityDistributionLandscape2021].
It is almost without human infrastructure, dominated by forest, and borders on a large nature reserve.
The study area has a mean elevation of \unit{438\,m} above sea level (range 223--711, IQR 351--509), and its mean slope at \unit{10\,m} resolution is 10.8° (IQR 4.6--15.1°).
In Norway's AR5 national land capability dataset [@ahlstromAR5Klassifikasjonssystem2019], \unit{1.5\,km^{2}} (4.5 %) of the study area is classified as mire --- defined as areas with mire vegetation and at least \unit{30\,cm} of peat depth.

At Ørskogfjellet we defined a study area of \unit{124\,km^{2}} which basically followed the footprint of the radiometric survey (Fig. \@ref(fig:sites)a). 
This study area comprises a wide range of major landscape types: *coastal plains*, *coastal fjord*, *inland valleys*, as well as *inland hills and mountains* [@simensenDiversityDistributionLandscape2021].
It is mostly forested, but also contains considerable farmland and open upland, and has several large lakes.
Its mean elevation is \unit{211\,m} above sea level (range 0--807, IQR 73--310), and its mean slope at \unit{10\,m} resolution is 13.0° (IQR 4.7--18.3°).
The AR5 dataset counts \unit{15.3\,km^{2}} (12.4 %) of the study area as mire.

>>>>

At Skrimfjella we delineated a study area of \unit{34\,km^{2}} based on radiometric coverage and accessibility (Fig. \@ref(fig:sites)b).
The study area has a diverse bedrock, with 32 % alkali feltspat granite, 26 % mergelstein, 10 % granite, and eight other types with > 1 % coverage (NGU, 1:250 000 dataset).
The landscape within our delineation is classified as *inland hills and mountains* [@simensenDiversityDistributionLandscape2021].
It is almost without human infrastructure, dominated by forest, and borders on a large nature reserve.
The study area has a mean elevation of \unit{438\,m} above sea level (range 223--711, IQR 351--509), and its mean slope at \unit{10\,m} resolution is 10.8° (IQR 4.6--15.1°).
In Norway's AR5 national land capability dataset [@ahlstromAR5Klassifikasjonssystem2019], \unit{1.5\,km^{2}} (4.5 %) of the study area is classified as mire --- defined as areas with mire vegetation and at least \unit{30\,cm} of peat depth.

At Ørskogfjellet we defined a study area of \unit{124\,km^{2}} which basically followed the footprint of the radiometric survey (Fig. \@ref(fig:sites)a).
According to the Geological Survey of Norway, bedrock in the area is 84 % granitic gneiss,  11 % granite, and 5 % aluminium silicate gneiss (NGU, 1:250 000 dataset). 
This study area comprises a wide range of major landscape types: *coastal plains*, *coastal fjord*, *inland valleys*, as well as *inland hills and mountains* [@simensenDiversityDistributionLandscape2021].
It is mostly forested, but also contains considerable farmland and open upland, and has several large lakes.
Its mean elevation is \unit{211\,m} above sea level (range 0--807, IQR 73--310), and its mean slope at \unit{10\,m} resolution is 13.0° (IQR 4.7--18.3°).
The AR5 dataset counts \unit{15.3\,km^{2}} (12.4 %) of the study area as mire.

### 2024-09-30 ms/ms.tex
ms: add bedrock to sites

At Skrimfjella we delineated a study area of \unit{34\,km^{2}} based on radiometric coverage and accessibility (Fig. \ref{fig:sites}b).\\
The landscape within our delineation is classified as \emph{inland hills and mountains} \citep{simensenDiversityDistributionLandscape2021}.
It is almost without human infrastructure, dominated by forest, and borders on a large nature reserve.
The study area has a mean elevation of \unit{438\,m} above sea level (range 223--711, IQR 351--509), and its mean slope at \unit{10\,m} resolution is 10.8° (IQR 4.6--15.1°).
In Norway's AR5 national land capability dataset \citep{ahlstromAR5Klassifikasjonssystem2019}, \unit{1.5\,km^{2}} (4.5 \%) of the study area is classified as mire --- defined as areas with mire vegetation and at least \unit{30\,cm} of peat depth.

At Ørskogfjellet we defined a study area of \unit{124\,km^{2}} which basically followed the footprint of the radiometric survey (Fig. \ref{fig:sites}a).
This study area comprises a wide range of major landscape types: \emph{coastal plains}, \emph{coastal fjord}, \emph{inland valleys}, as well as \emph{inland hills and mountains} \citep{simensenDiversityDistributionLandscape2021}.
It is mostly forested, but also contains considerable farmland and open upland, and has several large lakes.
Its mean elevation is \unit{211\,m} above sea level (range 0--807, IQR 73--310), and its mean slope at \unit{10\,m} resolution is 13.0° (IQR 4.7--18.3°).
The AR5 dataset counts \unit{15.3\,km^{2}} (12.4 \%) of the study area as mire.

>>>>

At Skrimfjella we delineated a study area of \unit{34\,km^{2}} based on radiometric coverage and accessibility (Fig. \ref{fig:sites}b).
The study area has a diverse bedrock, with 32 \% alkali feltspat granite, 26 \% mergelstein, 10 \% granite, and eight other types with \textgreater{} 1 \% coverage (NGU, 1:250 000 dataset).
The landscape within our delineation is classified as \emph{inland hills and mountains} \citep{simensenDiversityDistributionLandscape2021}.
It is almost without human infrastructure, dominated by forest, and borders on a large nature reserve.
The study area has a mean elevation of \unit{438\,m} above sea level (range 223--711, IQR 351--509), and its mean slope at \unit{10\,m} resolution is 10.8° (IQR 4.6--15.1°).
In Norway's AR5 national land capability dataset \citep{ahlstromAR5Klassifikasjonssystem2019}, \unit{1.5\,km^{2}} (4.5 \%) of the study area is classified as mire --- defined as areas with mire vegetation and at least \unit{30\,cm} of peat depth.

At Ørskogfjellet we defined a study area of \unit{124\,km^{2}} which basically followed the footprint of the radiometric survey (Fig. \ref{fig:sites}a).
According to the Geological Survey of Norway, bedrock in the area is 84 \% granitic gneiss, 11 \% granite, and 5 \% aluminium silicate gneiss (NGU, 1:250 000 dataset).
This study area comprises a wide range of major landscape types: \emph{coastal plains}, \emph{coastal fjord}, \emph{inland valleys}, as well as \emph{inland hills and mountains} \citep{simensenDiversityDistributionLandscape2021}.
It is mostly forested, but also contains considerable farmland and open upland, and has several large lakes.
Its mean elevation is \unit{211\,m} above sea level (range 0--807, IQR 73--310), and its mean slope at \unit{10\,m} resolution is 13.0° (IQR 4.7--18.3°).
The AR5 dataset counts \unit{15.3\,km^{2}} (12.4 \%) of the study area as mire.
